Influence of galaxy rotation and outflows in the Lyman Alpha spectral line

### 2016-04-13 paper/paper.tex

%Document Class
\documentclass{latex/emulateapj}
\usepackage{multirow,color,wrapfig,ulem}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.3\textwidth]{./figures/model}
	\end{center}
	\caption{\textbf{Model:} Spherical LAE with tangential and radial velocity due to rotation and outflows.
		\label{fig:model}}
\end{figure}

@@

\subsection{Galaxy's Viewing Angle}
An observer located far away, only receives photons emitted along its line of sight. That means, only photons escaping in the direction of the observer must be counted in the spectrum. In the simulation I approximate this by taking into account only the photons with escaping direction angle $\theta$ respect to the rotation axis within the range $[\theta_{min}-\theta_{max}]$. I illustrate this in Fig. \ref{fig:viewing_angle_sketch}. \\

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/viewing_angle_sketch}
	\end{center}
	\caption{\textbf{Viewing Angle Sketch:} The galaxy cut is in the $y-z$ plane perspective and the observer is located at an specific viewing angle of the sphere. Only photons with a direction that enters in this range of vision are taken into account to build the observed spectrum.
		\label{fig:viewing_angle_sketch}}
\end{figure}

@@

The resulting sets of spectra are in Figs. \ref{fig:3_tau10E5_phi83-90}, \ref{fig:3_tau10E7_phi83-90} and \ref{fig:3_tau10E6_phi83-90} for $\theta \simeq 90^\circ$. I do not include the spectra for \vout = 50, 75 \kms because they are similar to \vout = 25 \kms. For this reason, I limit in all the plots \vout to a maximum value of 25 \kms. Nevertheless, the figures for \vout = 50, 75 \kms are in the Appendix \ref{first_plots} in Figs. \ref{fig:2_tau10E5_phi83-90}, \ref{fig:2_tau10E6_phi83-90} and \ref{fig:2_tau10E7_phi83-90}.\\

\newpage

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/3_tau10E5_phi83-90}
	\end{center}
	\caption{\textbf{\lya profile for \tauh$=10^5$:} With \vrot ranging $50,100$ \kms and \vout ranging $5,10,15,20,25$ \kms. The intensity is in arbitrary units. The viewing angle $\theta \simeq 90^\circ$. The dashed vertical line indicates the \lya line's natural frequency. 
		\label{fig:3_tau10E5_phi83-90}}
\end{figure}

\newpage

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/3_tau10E6_phi83-90}
	\end{center}
	\caption{\textbf{\lya profile for \tauh$=10^6$:}  Same as Fig. \ref{fig:3_tau10E5_phi83-90} but for \tauh$=10^6$.
		\label{fig:3_tau10E6_phi83-90}}
\end{figure}

\newpage

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/3_tau10E7_phi83-90}
	\end{center}
	\caption{\textbf{\lya profile for \tauh$=10^7$:} Same as Fig. \ref{fig:3_tau10E5_phi83-90} but for \tauh$=10^7$.
		\label{fig:3_tau10E7_phi83-90}}
\end{figure}

\newpage

@@

All of this work is available online and free to use to anyone. The data, source code and instructions to replicate my monograph's results are in the GitHub repository:  \texttt{https://github.com/astroandes/CLARA\_RotationOutflows}. \\

@@

\newpage

@@

\appendix
\section{Additional Figures}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=1\textwidth]{./figures/appendix/2_tau10E5_phi83-90}
	\end{center}
	\caption{\textbf{\lya profile for \tauh$=10^5$:} With \vrot ranging $50,100$ \kms and \vout ranging $50,75$ \kms.
		\label{fig:2_tau10E5_phi83-90}}
\end{figure}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=1\textwidth]{./figures/appendix/2_tau10E6_phi83-90}
	\end{center}
	\caption{\textbf{\lya profile for \tauh$=10^6$:} With \vrot ranging $50,100$ \kms and \vout ranging $50,75$ \kms.
		\label{fig:2_tau10E6_phi83-90}}
\end{figure}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=1\textwidth]{./figures/appendix/2_tau10E7_phi83-90}
	\end{center}
	\caption{\textbf{\lya profile for \tauh$=10^7$:} With \vrot ranging $50,100$ \kms and \vout ranging $50,75$ \kms.
		\label{fig:2_tau10E7_phi83-90}}
\end{figure}

>>>>

%Document Class
\documentclass[twocolappendix]{latex/emulateapj}

@@

@@

\subsection{Galaxy's Viewing Angle}
An observer located far away, only receives photons emitted along its line of sight. That means, only photons escaping in the direction of the observer must be counted in the spectrum. In the simulation I approximate this by taking into account only the photons with escaping direction angle $\theta$ respect to the rotation axis within the range $[\theta_{min}-\theta_{max}]$. I illustrate this in Fig. \ref{fig:model}. \\

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.48\textwidth]{./figures/model}
	\end{center}
	\caption{\textbf{Model:} Spherical LAE with tangential and radial velocities due to rotation and outflows, respectively. The galaxy cut is in the $y-z$ plane perspective. The observer is located at an specific viewing angle of the sphere. Only photons with a direction that enters in this range of vision are taken into account to build the observed spectrum.
		\label{fig:model}}
\end{figure}

@@

The resulting sets of spectra are in Figs. \ref{fig:3_tau10E5_phi83-90}, \ref{fig:3_tau10E7_phi83-90} and \ref{fig:3_tau10E6_phi83-90} for $\theta \simeq 90^\circ$ available in the Appendix \ref{ap:results_figures}. I do not include the spectra for \vout = 50, 75 \kms because they are similar to \vout = 25 \kms. For this reason, I limit in all the plots \vout to a maximum value of 25 \kms. Nevertheless, the figures for \vout = 50, 75 \kms are in the Appendix \ref{ap:additional_figures} in Figs. \ref{fig:2_tau10E5_phi83-90}, \ref{fig:2_tau10E6_phi83-90} and \ref{fig:2_tau10E7_phi83-90}.\\

@@

All of this work is available online and free to use to anyone. The data, source code and instructions to replicate my monograph's results are in the GitHub repository:  \texttt{https://github.com/astroandes/CLARA\_RotationOut flows}. \\

@@

@@

\appendix

\begin{figure}[!htbp]
	\centering
	\begin{minipage}[b]{0.45\textwidth}
		\section{Results' Figures}
		\label{ap:results_figures}

		\includegraphics[width=\textwidth]{./figures/3_tau10E5_phi83-90}
		\caption{\textbf{\lya profile for \tauh$=10^5$:} With \vrot ranging $50,100$ \kms and \vout ranging $5,10,15,20,25$ \kms. The intensity is in arbitrary units. The viewing angle $\theta \simeq 90^\circ$. The dashed vertical line indicates the \lya line's natural frequency. 
			\label{fig:3_tau10E5_phi83-90}}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{./figures/3_tau10E6_phi83-90}
		\caption{\textbf{\lya profile for \tauh$=10^6$:}  Same as Fig. \ref{fig:3_tau10E5_phi83-90} but for \tauh$=10^6$. 
			\label{fig:3_tau10E6_phi83-90}}
		\vspace{1.5mm}
	\end{minipage}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\begin{minipage}[b]{0.45\textwidth}
		\vspace{3mm}
		\includegraphics[width=\textwidth]{./figures/3_tau10E7_phi83-90}
		\caption{\textbf{\lya profile for \tauh$=10^7$:} Same as Fig. \ref{fig:3_tau10E5_phi83-90} but for \tauh$=10^7$.
			\label{fig:3_tau10E7_phi83-90}}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\textwidth}
		\section{Additional Figures}
		\label{ap:additional_figures}

@@

		\vspace{2.7cm}

		\includegraphics[width=\textwidth]{./figures/appendix/2_tau10E5_phi83-90}
		\caption{\textbf{\lya profile for \tauh$=10^5$:} With \vrot ranging $50,100$ \kms and \vout ranging $50,75$ \kms.
			\label{fig:2_tau10E5_phi83-90}}
	\end{minipage}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\begin{minipage}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{./figures/appendix/2_tau10E6_phi83-90}
		\caption{\textbf{\lya profile for \tauh$=10^6$:} With \vrot ranging $50,100$ \kms and \vout ranging $50,75$ \kms.
			\label{fig:2_tau10E6_phi83-90}}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{./figures/appendix/2_tau10E7_phi83-90}
		\caption{\textbf{\lya profile for \tauh$=10^7$:} With \vrot ranging $50,100$ \kms and \vout ranging $50,75$ \kms.
			\label{fig:2_tau10E7_phi83-90}}
	\end{minipage}
\end{figure}
